An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-05-19 CMPSpaper_writing/CMPSpaper_writing.Rmd
tiny update

1. **cut the reference signature into consecutive, non-overlapping and equal-length basis segments:**
The command `get_segs(x, len=50)` implements this step:  it takes  bullet signature `x` in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.

>>>>

1. **cut the reference signature into consecutive, non-overlapping and equal-length basis segments:**
The command `get_segs(x, len=50)` implements this step:  it takes  bullet signature `x` in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`, which are referred as "basis segments".
